---
title: "PEI & PSQ Fielity reporting"
author: "Emma Elcombe"
#date written: "December, 2017"
output: word_document
---

```{r Setup, include = FALSE}

#Set up R environment and load the data

library(readxl)
library(foreign)
library(dplyr)
library(knitr)
library(ggplot2)
library(zoo)


# Get data
getwd()
PEI = read.csv("C:/Users/Tresi-Emma/Documents/R for MECSH/Load/PEI_Data.csv", sep = ",")
PSQ = read.csv("C:/Users/Tresi-Emma/Documents/R for MECSH/Load/PSQ_Data.csv", sep = "\t")

Today <- Sys.Date()
Extract_date <- as.Date(PEI$extract_date[1], "%Y-%m-%d")
```
Report date: &emsp;&emsp;&emsp;&emsp;&emsp;&emsp; **`r format(Today, "%d %b %Y")`**  
Date of last data extract: &emsp; `r format(Extract_date, "%d %b %Y")`

##### Set location

```{r Enter site for report, enter length for recent results}
w_site <- "Jersey"
```

##### Set number of 'recent' days

```{r Enter length for recent results}
w_days <- 90
```

## PEI

### Number of records for site and associated regions

```{r, PEI Basic Data, include=FALSE}
PEI_site <- PEI %>% filter(site == w_site)
Px_tot <- max(row(PEI_site))
PEI_region <- PEI_site %>% mutate(Region = region, Responses = 'Record count') %>% group_by(Region) %>% summarise(Responses=n())

temp <- PEI_region %>% filter(Region == "Base")
temp[,2]

```

To date there have been `r Px_tot` PEI responses recorded for `r w_site`. This includes `r temp[,2]` responses from the implementation phase of the project (labelled 'Base') and `r Px_tot - temp[,2]` responses since.

`r kable(PEI_region)`  

### Average and Target scores
#### All time

```{r PEI Overall average and target scores, include=FALSE}

tot_mean <- round(mean(PEI_site$PEI_total, na.rm = TRUE), digits = 2)
Over_4 <- PEI_site %>% filter(PEI_over4==TRUE) %>% group_by(site) %>% summarise(n=n())
Over_4_per <- round(as.numeric((Over_4[2]/Px_tot)*100), digits = 2)

```

Average PEI score recorded: **`r tot_mean`**.  
Percentage of participants scoring over 4 (cut off score): **`r Over_4_per`%**.  

#### Recent

```{r PEI Recent entries only, include=FALSE}

PEI_site$date <- as.Date(PEI_site$date, "%Y-%m-%d")
PEI_site$days <- difftime(as.Date(Today), PEI_site$date, c("auto"))
PEI_recent <- PEI_site %>% filter(days <= w_days)
Px_rec <- max(row(PEI_recent))

rec_mean <- round(mean(PEI_recent$PEI_total, na.rm = TRUE), digits = 2)
rec_Over_4 <- PEI_recent %>% filter(PEI_over4==TRUE) %>% group_by(site) %>% summarise(n=n())
rec_Over_4_per <- round(as.numeric((rec_Over_4[2]/Px_rec)*100), digits = 2)
```

During the previous `r w_days` days there have been `r Px_rec` records entered.  

Average PEI score recorded: **`r rec_mean`**.  
Percentage of participants scoring over 4 (cut off score): **`r rec_Over_4_per`%**.    

###Graphs

##### Number of responses per quarter 

```{r fig.width=7, fig.height=4, echo=FALSE}
PEI_site$qtr <- as.yearqtr(PEI_site$date, format = "%Y-%m-%d")
PEI_site$qtr <- as.factor(PEI_site$qtr)

ggplot(PEI_site, aes(x = qtr)) + geom_bar(fill = "Sky Blue", na.rm = TRUE) + ggtitle("Number of responses per quarter") + xlab("Year-Quarter")  

```




##### Average PEI scores 

```{r,  fig.width=7, fig.height=4, echo=FALSE}

PEI_mean_qtr <- PEI_site %>% group_by(qtr) %>% summarise(mean = mean(PEI_total, na.rm = TRUE), sd = sd(PEI_total, na.rm = TRUE))

ggplot(data=PEI_site, aes(x=date, y=PEI_total)) + 
  ylim(0,12) + 
  stat_smooth(colour='blue', span=1, method = 'loess', na.rm = TRUE) + 
  geom_hline(yintercept=4, linetype="dashed", color = "red", size=1) +
  geom_point(size = 2, na.rm = TRUE) + 
  ggtitle("PEI scores overtime") + xlab("Date") + ylab("PEI Score")

```



## PSQ

### Number of records for site and associated regions

```{r, PSQ Basic Data, include=FALSE}
PSQ_site <- PSQ %>% filter(site == w_site)
Px_tot <- max(row(PSQ_site))
PSQ_region <- PSQ_site %>% mutate(Region = region, Responses = 'Record count') %>% group_by(Region) %>% summarise(Responses=n())

temp <- PSQ_region %>% filter(Region == "Base")
temp[,2]

```

To date there have been `r Px_tot` PSQ responses recorded for `r w_site`. This includes `r temp[,2]` responses from the implementation phase of the project (labelled 'Base') and `r Px_tot - temp[,2]` responses since.

`r kable(PSQ_region)`  

### Average and Target scores
#### All time

```{r PSQ Overall average and target scores, include=FALSE}

tot_mean <- round(mean(PSQ_site$PSQ_total, na.rm = TRUE), digits = 2)
Under_20 <- PSQ_site %>% filter(PSQ_under20==TRUE) %>% group_by(site) %>% summarise(n=n())
Under_20_per <- round(as.numeric((Under_20[2]/Px_tot)*100), digits = 2)

```

Average PSQ score recorded: **`r tot_mean`**.  
Percentage of participants scoring under 20 (cut off score): **`r Under_20_per`%**.  

#### Recent

```{r PSQ Recent entries only, include=FALSE}


PSQ_site$date <- as.Date(PSQ_site$date, "%Y-%m-%d")
PSQ_site$days <- difftime(as.Date(Today), PSQ_site$date, c("auto"))
PSQ_recent <- PSQ_site %>% filter(days <= w_days)
Px_rec <- max(row(PSQ_recent))

rec_mean <- round(mean(PSQ_recent$PSQ_total, na.rm = TRUE), digits = 2)
rec_Under_20 <- PSQ_recent %>% filter(PSQ_under20==TRUE) %>% group_by(site) %>% summarise(n=n())
rec_Under_20_per <- round(as.numeric((rec_Under_20[2]/Px_rec)*100), digits = 2)
```

During the previous `r w_days` days there have been `r Px_rec` records entered.  

Average PSQ score reported is: **`r rec_mean`**.  
Percentage of participants scoring under 20 (cut off score): **`r rec_Under_20_per`%**.    

###Graphs

##### Number of responses per quarter 

```{r, fig.width=7, fig.height=4, echo=FALSE}
PSQ_site$qtr <- as.yearqtr(PSQ_site$date, format = "%Y-%m-%d")
PSQ_site$qtr <- as.factor(PSQ_site$qtr)

ggplot(PSQ_site, aes(x = qtr)) + geom_bar(fill = "Sky Blue") + ggtitle("Number of responses per quarter") + xlab("Year-Quarter")  

```


##### Average PSQ scores

```{r, fig.width=7, fig.height=4, echo=FALSE}

PSQ_mean_qtr <- PSQ_site %>% group_by(qtr) %>% summarise(mean = mean(PSQ_total, na.rm = TRUE), sd = sd(PSQ_total, na.rm = TRUE))

ggplot(data=PSQ_site, aes(x=date, y=PSQ_total)) + 
  ylim(10,30) + 
  stat_smooth(colour='blue', span=1, method = 'loess', na.rm = TRUE) + 
  geom_hline(yintercept=20, linetype="dashed", color = "red", size=1) +
  geom_point(na.rm = TRUE) + 
  ggtitle("PSQ scores over time") + xlab("Date") + ylab("PSQ score")
```



###End