---
output:
  word_document: default
  html_document: default
---

## eLearning

```{r setup, include=FALSE}

#Packages needed
library(readxl)
library(dplyr)
library(knitr)
library(tidyr)
library(futile.logger)

opts_knit$set(root.dir = "C:/Users/Tresi-Emma/Documents/R for MECSH")
#setwd("C:/Users/Tresi-Emma/Documents/R for MECSH")



```

# Logging

There are 3 levels of logging in this file TRACE (most words), INFO, and ERROR (least words)
 by default, script is logged at the INFO level
 All ERROR messages are also reported to Error folder, see log_and_quit().

```{r logging and error handling, include=FALSE}

# Logging
flog.appender(appender.file("Log/eLearning.log"), name='logger.c')
flog.info("START", name='logger.c')
flog.info("eLearning Started - Working Directory set", name='logger.c')

# set error handling.
log_and_quit <- function() {
  # Log error
  if(exists("err_msg")) {
    print('exists')
  } else {
    err_msg <- geterrmessage()
  }
  flog.error("Fatal Error: %s", err_msg, name='logger.c')
  setwd("C:/Users/Tresi-Emma/Documents/Interfaces")
  flog.appender(appender.file("eLearning.txt"), name='logger.a')
  flog.info("Failure", name='logger.a')
  setwd("C:/Users/Tresi-Emma/Desktop")
  flog.appender(appender.file("eLearning FAILED.log"), name='logger.b')
  flog.error("PEI Fetch failed: %s", err_msg, name='logger.b')
  setwd("C:/Users/Tresi-Emma/Documents/R for MECSH")
}
options(error = log_and_quit)

```

# Load elearning data 

Data is loaded from the 'R for MECSH/Load' folder. 
It arrives in this folder from the eLearnign website

```{r data loading}

#Load eLearning file
courseData <- read_excel("Load/Victoria-eLearning.xlsx", sheet = "Victoria-Current")

#Table creation - these steps are unlikely to be needed in the future, as 3 raw tables will arive, not 1 merged table.

ID_status <- courseData[c("NurseID","Location",
                        "C1Completed On","C1Status","C2Status","C3Status","C4Status",
                        "C5Status","C6Status","C6Completed On")]

# only because test load file has extra rows
ID_status <- ID_status[1:29,1:10]

ID_px <- courseData[c("NurseID","Location","LICENSEE GROUP NAME","T3NOTES","FirstName","LastName",
                      "FPM Completed", "Position", "Position2" )]

```

##Completion statuses are calculated and checked for errors


```{r elearning completion status calucations, include=FALSE}

#Completed
ID_status$C1 <- match(ID_status$C1Status, "Completed", nomatch = 0)
ID_status$C2 <- match(ID_status$C2Status, "Completed", nomatch = 0)
ID_status$C3 <- match(ID_status$C3Status, "Completed", nomatch = 0)
ID_status$C4 <- match(ID_status$C4Status, "Completed", nomatch = 0)
ID_status$C5 <- match(ID_status$C5Status, "Completed", nomatch = 0)
ID_status$C6 <- match(ID_status$C6Status, "Completed", nomatch = 0)
ID_status$total_comp <- rowSums(ID_status[c(11:16)])

#Incomplete
ID_status$C1 <- match(ID_status$C1Status, "Incomplete", nomatch = 0)
ID_status$C2 <- match(ID_status$C2Status, "Incomplete", nomatch = 0)
ID_status$C3 <- match(ID_status$C3Status, "Incomplete", nomatch = 0)
ID_status$C4 <- match(ID_status$C4Status, "Incomplete", nomatch = 0)
ID_status$C5 <- match(ID_status$C5Status, "Incomplete", nomatch = 0)
ID_status$C6 <- match(ID_status$C6Status, "Incomplete", nomatch = 0)
ID_status$total_Incomp <- rowSums(ID_status[c(11:16)])

#Not attempted
ID_status$C1 <- match(ID_status$C1Status, "Not Attempted", nomatch = 0)
ID_status$C2 <- match(ID_status$C2Status, "Not Attempted", nomatch = 0)
ID_status$C3 <- match(ID_status$C3Status, "Not Attempted", nomatch = 0)
ID_status$C4 <- match(ID_status$C4Status, "Not Attempted", nomatch = 0)
ID_status$C5 <- match(ID_status$C5Status, "Not Attempted", nomatch = 0)
ID_status$C6 <- match(ID_status$C6Status, "Not Attempted", nomatch = 0)
ID_status$total_NotAtmpt <- rowSums(ID_status[c(11:16)])

#check all equal 6
ID_status$CHECK <- rowSums(ID_status[c(17:19)])
Avg_cnt <- mean(ID_status$CHECK, na.rm = TRUE)
if (Avg_cnt != 6){
    flog.error("CHECKING failed", name='logger.c')
    err_msg <- "CHECKING failed"
    log_and_quit()
  } else {
    flog.info("CHECKING passed", name='logger.c')
}

# outcome columns
ID_status$COMPLETED <- match(ID_status$total_comp==6,1,0)
ID_status$STATUS <- ifelse(ID_status$total_comp==6, "Completed", ifelse(ID_status$total_Incomp>0, "Started", "Not Attempted"))

#clean up
ID_status$C1 <- NULL
ID_status$C2 <- NULL
ID_status$C3 <- NULL
ID_status$C4 <- NULL
ID_status$C5 <- NULL
ID_status$C6 <- NULL
ID_status$CHECK <- NULL


```



```{r TEST ONLY, include=FALSE}
#TEST ONLY
#Ensure all data is included in summary table

# All Staff
All_Staff <- ID_status %>% group_by(Location) %>% 
  select(Location, COMPLETED) %>% summarise (n=n(), perc_comp = mean(COMPLETED)*100)
All_Staff

if ((count(ID_status) - sum(All_Staff$n)) != 0){
    flog.error("CHECKING failed", name='logger.c')
    err_msg <- "CHECKING failed"
    log_and_quit()
  } else {
    flog.info("CHECKING passed", name='logger.c')
}

```

# Training status by site
traing status has been grouped into 1 of 3 categories, Not Atempted, Started and Completed. 
This table shows the number of staff in each category for each site. 
All staff members in eLeanring system are included in this table.

```{r Training status by site}
Site_status <- ID_status %>% group_by(Location, STATUS) %>% 
  select(Location, COMPLETED, STATUS) %>% summarise (n=n())

Site_status <- ungroup(spread(Site_status, STATUS, n, fill = 0))
Site_status$Total_Staff <- rowSums(Site_status[c(2:4)])
Site_status <- rbind(Site_status, c("Total", colSums(Site_status[,2:5])))
Site_status

```

# Join to Nurse details table
eLearning data joined with Staff data

```{r}
trim_px <- ID_px[,c(1,7,9)]

Staff_type <- ID_status %>% left_join(trim_px,by = "NurseID")

```

#Data cleaned and main reference table produced
This table is used for all further summaries/reports

```{r Cleaning and formatting, include=FALSE}
# clean and re-format data fields
Staff_type$Strt_date <- as.Date(substr(Staff_type$`C1Completed On`,1,10), "%Y-%m-%d")
Staff_type$Strt_yr <- as.numeric(substr(Staff_type$`C1Completed On`,1,4), "%Y")
Staff_type$pre_2016 <- if_else(Staff_type$Strt_yr<2016, "TRUE", "FALSE", missing = "Unknown")
Staff_type$sees_clients <- if_else((Staff_type$Position2=="Nurse"|Staff_type$Position2=="SW"), "Nurse_SW", "Other", missing = "Unknown")

# drop un-needed columns
Staff_status <- Staff_type[c("NurseID","Location","Strt_date","pre_2016","COMPLETED", "STATUS","FPM Completed",  "sees_clients")]
Staff_status

```
```{r}
Staff_status
```


#Main Outcomes - Full table


```{r}
# Full table
Full_table <- Staff_status %>%  group_by(pre_2016, Location, sees_clients) %>% 
  select(pre_2016, Location, sees_clients, COMPLETED) %>% summarise (n=n())
Full_table = ungroup(spread(Full_table, sees_clients, n, fill = 0))
Full_table$Total_Staff <- rowSums(Full_table[c("Nurse_SW", "Other")])

# check all rows account for
if ((count(ID_status) - colSums(Full_table[,5])) != 0){
    flog.error("CHECKING failed", name='logger.c')
    err_msg <- "CHECKING failed"
    log_and_quit()
  } else {
    flog.info("CHECKING passed", name='logger.c')
}

#Show result
Full_table <- rbind(Full_table, c("Total", "", colSums(Full_table[,3:5])))
Full_table

```

Main Outcomes - nurses per category - position and training time


```{r}
# nurses per category - position and training time

sum_count <- Staff_status %>%  group_by(pre_2016, sees_clients) %>% 
  select(pre_2016, sees_clients, COMPLETED) %>% summarise (n=n())
sum_count <- ungroup(spread(sum_count, sees_clients, n, fill = 0))
sum_count$Total_Staff <- rowSums(sum_count[c("Nurse_SW", "Other")])
sum_count <- rbind(sum_count, c("Total", colSums(sum_count[,2:4])))
sum_count

```

Main Outcomes - Summary table

```{r}

# Summary table - filtered for position and training time

Filtered_table <- Staff_status %>% filter(pre_2016 == "TRUE" & sees_clients == "Nurse_SW") %>% group_by(Location) %>% select(Location, COMPLETED) %>% summarise (n=n(), perc_comp = mean(COMPLETED)*100)
Filtered_table <- rbind(Filtered_table, c("Total", colSums(Filtered_table[,2]), colMeans(Filtered_table[,3])))
Filtered_table
```

