---
output:
  word_document: default
  html_document: default
---


```{r set up, include=FALSE}

library(readxl)
library(dplyr)
library(knitr)
library(tidyr)
library(lubridate)
library(ggplot2)
setwd("C:/R")
```


## PART A - Load raw data files

####Load base file 
```{r, include=FALSE}
rm(data)
data <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Cooma Q1")

temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Cooma Q2")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Cooma Q3")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Cooma Q4")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Bombala FinY")
data <- rbind(data, temp)

temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Braidwood FinY")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Crookwell FinY")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "Delegate FinY")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 1 2016_2017_AG 6.xlsx", sheet = "QB FinY")
data <- rbind(data, temp)

temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "BV Q1_2")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "BV Q3_4")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "EB Q1_2")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "EB Q3_4")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "GB Q1_2")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "GB Q3_4")
data <- rbind(data, temp)
temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 2 2016_2017_AG 6.xlsx", sheet = "Yass")
data <- rbind(data, temp)

temp <- read_excel("C:/R/Rprojects/MECSH/sSouthernNSW/raw_data/MESCH Reports_SNSWLHD_Part 3 AbH services 2016_2017_AG 6.xlsx", sheet = "EB AbH FinY")
data <- rbind(data, temp)
rm(temp)
```

`r nrow(data)` rows of data loaded.  

 

```{r, , include=FALSE}
data$site <- substring(data$FACILITY,1,6)
site_summ <- data %>% group_by(site) %>% summarise(n=n())
```
 
#### Clean data

```{r create summary table with only variables needed, include=FALSE}
data_summ <- data[c("DATE_RANGE","site","MRN","DOB","REG_DT_TM","REFERRAL_RECEIPT_DT","DISCH_DT_TM", "POWERFORM_NAME","POWERFORM_DT_TM","SERVICE_DELIVERY_MODE","MOS_DURATION","SERV_START_DT_TM","FORM_ID","ENCNTR_ID")]

# remove 'no client contact' rows from the Service_Delivery_Mode column
data_clean <- data_summ %>% filter(substr(SERVICE_DELIVERY_MODE,1,18) != "No Client Contact ") 
rows_NoContact <- sum(substr(data_summ$SERVICE_DELIVERY_MODE,1,18)== "No Client Contact ")

# number of duplicate rows remaining
temp <- data_clean %>% group_by(site, MRN, SERV_START_DT_TM) %>% summarise(n=n()) %>% filter(n>1) 
rows_SameDay <- nrow(temp)

data_clean$dup <- duplicated(data_clean[c("site", "MRN", "SERV_START_DT_TM")])

rows_dups <- sum(data_clean$dup)

data_clean <- data_clean %>% filter(dup == FALSE)

```
  
Step 1: remove invalid records

In total `r rows_NoContact` rows had a 'service delivery mode' starting with 'No Client Contact'. These records were removed. Of the remaining records there were `r rows_SameDay` sets of duplicate records, ie records that occured on the same day for the same Mother/family.   
For this report, records were de-duplified in a random fashion (ie not based on any particular variable), with a total of `r rows_dups` records being removed.   

These process left a total of `r nrow(data_clean)` records remaining.  
  

### Summary data

#### Participants per site, and visits per particpant

```{r, include=FALSE}
Px_vis_summary <- data_clean %>% group_by(site, MRN) %>% summarise(visit_count=n())
#data_summ %>% group_by(site, MRN, ENCNTR_ID) %>% summarise(visit_count=n())
# if both tables above produce the same number of rows we can assume that encounter ID is paried 1 to 1 with MRN.

Px_summary <- Px_vis_summary %>% group_by(site) %>% summarise("Number of Participants"=n(), total_visits = sum(visit_count), "Avg visits per px"= round(mean(visit_count), digits=2))

```

##### Participant summary table

`r kable(Px_summary)`


### Participant details

```{r, include=FALSE}
rows_px <- data_clean %>% group_by(site, MRN) %>% summarise(n=n())
Px_data <- data_clean %>% group_by(site, MRN, DOB, REG_DT_TM, DISCH_DT_TM) %>% summarise(DateFirstVisit=min(SERV_START_DT_TM), DateLastVisit=max(SERV_START_DT_TM),VisitCount=n())

# Enrollment
Enroll <- Px_data %>% select(site, REG_DT_TM) %>% mutate(qtr = as.character(quarter(REG_DT_TM, with_year = TRUE))) %>% group_by(site, qtr) %>%  summarise(count=n())

```

In total there are `r nrow(rows_px)` participants who have recived a Home visit for MECSH in Southern NSW LHD.  

The following graph shows the number of participants that have been visited at least once in Southern NSW LHD. It is based off the registration date (REG_DT_TM) and only includes those participants whose visits were allocated to associate grp6.

```{r, echo=FALSE}

ggplot(data=Enroll, aes(x=qtr, y=count, group=site, colour=site)) +
    geom_line() +
    geom_point() +
    xlab("Year.Quater") + ylab("px enrolled") + ggtitle("Number of Px enrolled each Qtr")

```

  
  
To be able to conduct a more complete analysis the following are needed:  
A. A full list of participants (the data provided so far does not show the participants which are/were enrolled, but have not yet been seen)  
B. Mother Due Date (EDD)  
C. Child Date of Birth  


### Home visit details

The following graph shows the number of home visits completed by each site per quarter.  
If no dot can be seen for a quarter, the number of visits was zero.  


```{r, echo=FALSE}

HV_data <- data_clean %>% mutate(qtr = as.character(quarter(REG_DT_TM, with_year = TRUE))) %>% group_by(site, qtr) %>% summarise(VisitCount=n()) 

# Enrollment
Enroll <- Px_data %>% mutate(qtr = as.character(quarter(REG_DT_TM, with_year = TRUE))) %>% group_by(site, qtr) %>%  summarise(count=n())

ggplot(data=HV_data, aes(x=qtr, y=VisitCount, group=site, colour=site)) +
    geom_line() +
    geom_point() +
    xlab("Year.Quater") + ylab("number of visits per quarter") + ggtitle("Number of Home Visits recorded each Qtr")

```

##### Participant detail table

```{r, include=FALSE}
Px_data$REG_DT_TM <- round(Px_data$REG_DT_TM, "day")
Px_data$DateFirstVisit <- round(Px_data$DateFirstVisit, "day")
Px_data$DateLastVisit <- round(Px_data$DateLastVisit, "day")
#Px_data$Px_disch <- if(!is.na(Px_data$DISCH_DT_TM)) "discharged"

```


`r kable(Px_data)`


