---
title: "MECSH r@h Antecedents refined"
author: "Emma Elcombe"
date: "December, 2017"
output: word_document
params:
   Vars: !r c(2,14,35)
   topic: !r "Drugs and Alcohol"
---

## MECSH r@h Disclosures

Set up R environment and load data home visit data (SPSS_r@h - v11), and disclosure data (srf 050917 v11)


```{r Setup, include = FALSE}
library(stats)
library(readxl)
library(foreign)
library(tidyr)
library(dplyr)
library(knitr)
library(ggplot2)


# Get data
setwd("//ad.uws.edu.au/dfshare/HomesCMB$/30042685/My Documents/MECSH/By Site/r@h/Nurse home visit activity data")
getwd()
SPSS_v11 = read.spss("SPSS_r@h_June17 - v11 merged dups.sav", to.data.frame=TRUE, use.value.labels = TRUE)
setwd("//ad.uws.edu.au/dfshare/HomesCMB$/30042685/My Documents/MECSH/By Site/r@h/Risk Factors/Mother vulnerablity data")
SPSS_srf = read.spss("srf 050917 v10 EE - taller v2.sav", to.data.frame=TRUE, use.value.labels = TRUE)
setwd("C:/R")
```

### number of particpants in each file

```{r, include=FALSE}

Px_v11 <- SPSS_v11 %>% group_by(ResearchID) %>% summarise(VisitCount=n())
Px_srf <- SPSS_srf %>% group_by(ResearchID, RiskRecorded) %>% summarise(n=n()) %>% spread(RiskRecorded,n )
A.Rows_Px_v11 <- max(row(Px_v11))
B.Rows_Px_srf <- max(row(Px_srf))
```

Number of participants in 'r@h RCT' file = `r A.Rows_Px_v11`  
Number of participants in srf file = `r B.Rows_Px_srf`   


### Risks per mother

```{r, include=FALSE}
Px_risks <- SPSS_srf %>% group_by(ResearchID, RiskRecorded) %>% summarise(n=n()) %>% spread(RiskRecorded,n ) 
Px_risks <- Px_risks %>% group_by(Yes) %>% summarise(n=n())
# replace missing with zero
Px_risks$Yes[is.na(Px_risks$Yes)] <- 0

ggplot(Px_risks, aes(x=Yes, y=n)) + geom_step() + ggtitle("Disclosures per mother") + xlab("number of disclosures") + ylab("number of mothers")

C.Px_no_risk <- as.integer(Px_risks[max(row(Px_risks)),2])

```

Disclosures were recorded for `r B.Rows_Px_srf - C.Px_no_risk` of the `r B.Rows_Px_srf`  participants


##### Clean vulnerability data

The full details of this are in the word document and SPSS data and syntax files within the directory 'C:/Users/Documents/MECSH/By Site/r@h/Risk Factors/Mother vulnerability data'.  In short, data was included if the column 'IncludeData' equaled 'Yes'.

```{r, include=FALSE}
df_srf <- SPSS_srf %>% filter(IncludeData == "Yes")
D.Rows_df_srf <- nrow(df_srf)
Px_df_srf <- df_srf %>% group_by(ResearchID) %>% summarise(n=n()) 
#Px_df_srf %>% group_by(n) %>% summarise(r=n()) 
E.Rows_Px_srf <- max(row(Px_df_srf))
```

##### Result of cleaning

Once data was cleaned to remove participants (2) with case records too complex to work with in this analysis, and records without dates (or dates which occurred too early). There were `r D.Rows_df_srf` records for `r E.Rows_Px_srf` participants remaining  

NOTE: This still includes disclosures made prior to Home Visits occurring.

#### Distribution of risk disclosure

```{r, echo=FALSE}
ggplot(Px_risks, aes(x=Yes, y=n)) + geom_col(fill = "sky blue") + ggtitle("Disclosures per mother") + xlab("number of disclosures") + ylab("number of mothers")

```



### Risks Disclosed - by category

```{r, include=FALSE}
Risk_tbl <- SPSS_srf %>% filter(IncludeData == "Yes") %>% group_by(Regarding, Risk_Factor) %>% summarise(n=n()) %>% spread(Regarding, n)
#Risk_tbl <- rbind(Risk_tbl, data.frame(Risk_Factor="Total",t(colSums(Risk_tbl[,-1]))))
Risk_tbl$Total <- rowSums(Risk_tbl[2:4], na.rm = TRUE )
Risk_tbl$Row <- seq.int(nrow(Risk_tbl))
Risk_tbl <- Risk_tbl[c(6,1,2,3,4,5)]

```

The following data was disclosed by mothers or parents to the nurse home visitors.   

Risks Recorded `r kable(Risk_tbl)`


### Home Visit data

##### Cleaning SPSS_v11 HV table

```{r, include=FALSE}
v11_summ <- SPSS_v11 %>% select(Valid_Check_new, Valid_new) %>% group_by(Valid_Check_new, Valid_new) %>% summarise(n=n()) %>% spread(Valid_new, n)
#v10_summ <- rbind(v10_summ, data.frame(Valid_Check_new="Total",t(colSums(v10_summ[,-1]))))
SPSS_HV <- SPSS_v11 %>% filter(as.numeric(Valid_Check_new) %in% c(1,6,7,8,9,10))
  # trim SPSS HV file
  SPSS_HV <- SPSS_HV[c(1:10,31, 32,35,214:231, 250, 256:297)]
  sum(duplicated(SPSS_HV$Table_ID))
```

In the Full SPSS data set from MCRI there are `r nrow(SPSS_v11)` rows of data.   

`r kable(v11_summ)`  

After removing the records flagged as A.Missing, B.No Visit content, c.Low act, Group session and D.Failure to attend. There are `r nrow(SPSS_HV)` rows which will be considered in this analysis.  



### Antecedents of disclosure

##### aim of code

Determine if the activities which occurred in the HV's just prior to disclosure, or at disclosure' were different from the activities which occurred at other times in the program.

For each disclosure determine  
 a. if it was made AN or PN  
 b. if it happened prior to a Home Visit (HV occurring)  
 c. which rows in the HV table happened at disclosure, and  
 d. which row/s happened before
 
 Record results, based on chronological date
 allow for some rows in HV table to fall into multiple categories (as risks can be disclosed more than once by the same mother/family)


##### logic of code

A. Identify all disclosures for given topic

B. For each disclosure determine  
 i. if it happened prior to first HV (remove if they did)  
 ii. if it was made AN or PN  
 iii. which rows in the HV table happened before  
 iv. which row/s happened at the event

C. return HV records and incremental counts for all searches (i to iv)

D. bind two sets of records (iii, iv), 

E. delete the records which occur twice, keeping the 'At' record where possible.

F. join this data to main HV table

G. analyse odds of activity occurring in the 3 separate categories (Normal, At or Before)

### `r params$topic`

##### A. Create table of disclosures
```{r, include=FALSE}

get_disclosures <- function(Vars){
  var_rcd <- df_srf %>% filter(as.numeric(Risk_Factor) %in% Vars)
  return(var_rcd)
}
var_list <- as.data.frame(Risk_tbl)[c(params$Vars),2]
var_rcd <- get_disclosures(params$Vars)
age_disc <- mean(var_rcd$Age_at_Disclosure)

  F.disc_rows <- nrow(var_rcd)
  Px_var <- var_rcd %>% group_by(ResearchID) %>% summarise(count=n())
  G.Px_var <- nrow(Px_var)

```


In total, `r F.disc_rows` records were returned for `r params$topic` (`r var_list`).    
This includes disclosures for `r G.Px_var` Families.  



##### B, C and D. Find HV records, label and return, bind
```{r, include=FALSE}

SPSS_HV_trim <- SPSS_HV[c("Table_ID","ResearchID","date_of_visit","Count_All_Activities")]

  # for each site...
  get_site_data <- function(DV_rcd_df,row_num) {
    # get the ID and Date
    Px_id <- DV_rcd_df[row_num,]$ResearchID
    Date_Dsc <- DV_rcd_df[row_num,]$DateDisclosed_Single
    # get data before disclosure
    before_df <- SPSS_HV_trim %>% filter(ResearchID == Px_id & date_of_visit < Date_Dsc) %>% arrange(desc(date_of_visit))
    if(nrow(before_df) > 0) before_df$PreHV <- seq.int(nrow(before_df))
    Px_Bf_cnt <- nrow(before_df)
    # get data at disclosure
    at_df <- SPSS_HV_trim %>% filter(ResearchID == Px_id & date_of_visit == Date_Dsc) %>% arrange(desc(date_of_visit))
    if(nrow(at_df) > 0) at_df$PreHV <- 0
    Px_At_cnt <- nrow(at_df)
    # return the dataframe
    return(list(before_df, Px_Bf_cnt, at_df, Px_At_cnt))
  }

try(rm(fetched_data, before_df, Px_Bf_cnt, at_df, Px_At_cnt))

for (i in seq_len(F.disc_rows)) {
      if (exists("fetched_data")) {
        fetched_data <- rbind(fetched_data, get_site_data(var_rcd,i)[[1]])
        fetched_data <- rbind(fetched_data, get_site_data(var_rcd,i)[[3]])
       } else {
        fetched_data <- get_site_data(var_rcd,i)[[1]]
        fetched_data <- rbind(fetched_data, get_site_data(var_rcd,i)[[3]])
      }
  if (exists("Px_Bf_cnt")) {
        Px_Bf_cnt <- rbind(Px_Bf_cnt, get_site_data(var_rcd,i)[[2]])
        } else {
        Px_Bf_cnt <- get_site_data(var_rcd,i)[[2]]
        }
  if (exists("Px_At_cnt")) {
        Px_At_cnt <- rbind(Px_At_cnt, get_site_data(var_rcd,i)[[4]])
      } else {
        Px_At_cnt <- get_site_data(var_rcd,i)[[4]]
      }
    } 

var_rcd$Px_Bf_cnt <- as.numeric(Px_Bf_cnt)
var_rcd$Px_At_cnt <- as.numeric(Px_At_cnt)
#move Px_.._cnt columns to front
var_rcd <- var_rcd[c(37,38,1:36)]
sum(fetched_data$PreHV==1)
HVs_disc <- fetched_data  %>% group_by(ResearchID) %>% summarise(n=n(), max=max(PreHV))
H.All_Rows <- nrow(fetched_data)

var_rcd$anyPreHV <- as.character(ifelse(Px_At_cnt==0 & Px_Bf_cnt == 0,"No HVs","HVs"))
age_disc <- var_rcd %>% group_by(anyPreHV) %>% summarise(count=n(), "mean age"=round(mean(Age_at_Disclosure), digits = 2), min=round(min(Age_at_Disclosure), digits = 2), max=round(max(Age_at_Disclosure), digits = 2))
AN_disc <- sum(var_rcd$Disclosure_Age_Band=="Antenatal" & var_rcd$anyPreHV=="HVs")
PN_disc <- sum(var_rcd$Disclosure_Age_Band!="Antenatal" & var_rcd$anyPreHV=="HVs")
HVs_disc <- var_rcd %>% mutate(PreHVs=Px_At_cnt + Px_Bf_cnt) %>% filter(PreHVs>0)

```


In total, `r H.All_Rows` HV's occurred on the day or prior to these disclosures.   
This includes `r colSums(Px_At_cnt)` on the day of disclosure, and `r colSums(Px_Bf_cnt)` before.  


#### Distribution of disclosures

Of the `r F.disc_rows` records were returned for `r params$topic` (`r var_list`). There were `r sum(var_rcd$anyPreHV=="No HVs")` disclosures which occurred prior to the first HV.

```{r, include=FALSE}
  Px_var <- HVs_disc %>% group_by(ResearchID) %>% summarise(count=n())
  G.Px_var <- nrow(Px_var)
  Px_var_dist <- Px_var %>% group_by(count) %>% summarise(n=n())
  Px_var_dist <- rbind(Px_var_dist, data.frame(count="Total",t(colSums(Px_var_dist[,-1]))))
```

Not including these, there were `r F.disc_rows - sum(var_rcd$anyPreHV=="No HVs")` disclosures for `r G.Px_var` Families.  

Distribution of disclosures by family `r kable(Px_var_dist)`




#### Disclosure by Home Visits  

The total number of home visits prior to (or at) disclosure was `r H.All_Rows`.  
The average number of Home visits per family prior to disclosure was `r round(mean(HVs_disc$PreHVs), digits=2)`.  

```{r, echo=FALSE}

ggplot(HVs_disc, aes(PreHVs)) + geom_histogram(binwidth = 2, fill = "sky blue", color = "DeepSkyBlue") + labs(x="HVs at Disclosure", title = "Distribution of disclosure by count of preceeding HVs") 

```
   
#### Age of the child at disclosure  

`r AN_disc` disclosures happened during the AN period, while `r PN_disc` disclosures happened after birth.  

Child age by the existence of Previous HV's  
`r kable(age_disc)`

```{r, echo=FALSE}

ggplot(var_rcd, aes(Age_at_Disclosure, fill = anyPreHV)) + geom_histogram(binwidth = 6, color = "dark blue") + labs(x="Age at Disclosure (weeks)", title = "Distribution of disclosure by child age")

```



##### E. trim HV records and remove duplicates.
```{r, include=FALSE}
# filter for 'day of' and 'previous 3' records
Pre_disc_act <- fetched_data %>% filter(PreHV <= 3) 
I.Rows_pre_disc <- nrow(Pre_disc_act)
J.Rows_At <- nrow(Pre_disc_act %>% filter(PreHV==0))
K.Rows_Bf <- nrow(Pre_disc_act %>% filter(PreHV>0))


#remove duplicates
L.test_dups <- sum(duplicated(Pre_disc_act$Table_ID))
Pre_disc_act <- Pre_disc_act %>% mutate(dups = duplicated(Pre_disc_act[,1:4])) %>% filter(dups==FALSE)
M.Rows_pre_disc <- nrow(Pre_disc_act)

spss2date <- function(x) as.Date(x/86400, origin = "1582-10-14")
Pre_disc_act$date_of_visit <- spss2date(Pre_disc_act$date_of_visit)

N.Rows_At <- nrow(Pre_disc_act %>% filter(PreHV==0))
O.Rows_Bf <- nrow(Pre_disc_act %>% filter(PreHV>0))

```

HV records were filtered to include only the HVs that occurred on the day of disclosure, or in one of the (up to) three visits which occurred prior.  
This left `r  I.Rows_pre_disc` HV records, including `r J.Rows_At` on the day of disclosure, and `r K.Rows_Bf` before.  
After removing the HV's that occur twice (due to multiple disclosures), there are `r M.Rows_pre_disc` HVs remaining to analyse.  This includes `r N.Rows_At` on the day of disclosure, and `r O.Rows_Bf` before.  
CHECK: The difference between `r  I.Rows_pre_disc` and `r M.Rows_pre_disc` should be `r L.test_dups` (the number of duplicates).
  
    
##### F. join this data to main HV table

```{r, include=FALSE}

# check there are no duplicates in fetched data
P.test_dups <- sum(duplicated(Pre_disc_act$Table_ID))

merged <- SPSS_HV %>% left_join(Pre_disc_act[c(1,2,5)], by = "Table_ID")
merged$Category <- "Normal"
merged$Category <- as.factor(ifelse(is.na(merged$PreHV), "Normal", 
                ifelse(merged$PreHV == 0, "At", 
                  ifelse(merged$PreHV > 0, "Before","CHECK"))))
merged$Bi_Categ <- as.factor(ifelse(is.na(merged$PreHV), "Normal","Associated"))
HV_type <- merged %>% group_by(ResearchID.x, Category) %>% summarise(HVs=n()) %>% group_by(Category) %>% summarise(Participants=n(), HVs=sum(HVs))
HV_type <- rbind(HV_type, data.frame(Category="Total",t(colSums(HV_type[,-1]))))
```

CHECK: This value should be zero: `r P.test_dups`.  

This table shows the number of participants with HV's, and the total number of HV's in each of the 3 categories.   
`r kable(HV_type)`   

NOTE: HV's should add to `r nrow(SPSS_HV)`, Participants columns will add to more than the total number of total number of participants as many will have HV's in multiple categories.
  
### Odds Ratios  

##### G. analyse odds of activity occuring in the 3 seperate categories (Not Associated, At or Before)


The table shown above has three categories for Home Visits. For this round of analyses the Home Visits which occurred At and Before the disclosure have been combined into 1 group.  All Home Visits are therefore categorised as either, associated with disclosure (Ass) or not associated with disclosure (normal).

example 2x2 contingency table for: `r params$topic` by activity 'mat_well_4'.

```{r, include=FALSE}
#pre data table
temp <- merged %>% select(Bi_Categ,inf_well_1:env_res_5,planning_1:tools_9)

eg <- temp %>% group_by(Bi_Categ, mat_well_4) %>% summarise(n=n()) %>% spread(mat_well_4,n)
  perc_yes_ass <- round(eg[1,3]/(eg[1,3]+eg[1,2])*100, digits = 2)
  perc_yes_norm <- round((eg[2,3])/(eg[2,3]+eg[2,2])*100, digits = 2)
eg <- rbind(data.frame(eg), data.frame(Bi_Categ="Total",t(colSums(eg[,-1]))))
eg$total <- rowSums(eg[,-1])
colnames(eg)[2] <- c("No")
```

`r kable(eg)`  
  
The contingency table is used to generate the percentage of 'Yes' responses in the associated group (e.g. Yes/(Yes+No)*100 = `r perc_yes_ass`), and the percentage of Yes's in the Normal or not associated group = `r perc_yes_norm`.  
  
The contingency table has also been used to determine the Odds Ratio (OR) using the formula: OR = (a/b)/(c/d) = ((Ass + Yes)/(Ass + No))/((Norm + Yes)/(Norm + No)).

```{r, include=FALSE}

odds_ratio_val <- data.frame(activity=0, ass_perc=0, norm_perc=0, OddsRatio=0)

#testing only
temp %>% group_by(Bi_Categ, ref_3) %>% summarise(n=n()) 

#loop for all activities
for (i in  2 : ncol(temp)) {
  temp_df <- temp %>% group_by(Bi_Categ, temp[,i]) %>% summarise(n=n()) 
  perc_yes_ass <- round(temp_df[2,"n"]/(temp_df[1,"n"]+temp_df[2,"n"])*100, digits = 2)
  perc_yes_norm <- round((temp_df[4,"n"])/(temp_df[3,"n"]+temp_df[4,"n"])*100, digits = 2)
  #OR = (a/b)/(c/d) = ((Ass + Yes)/(Ass + No))/((Norm + Yes)/(Norm + No))
  OR <- round(((temp_df[2,"n"])/(temp_df[1,"n"]))/((temp_df[4,"n"])/(temp_df[3,"n"])), digits = 2)
 odds_ratio_val[i,4] <- OR
 odds_ratio_val[i,1] <- colnames(temp[i])
 odds_ratio_val[i,2] <- perc_yes_ass
 odds_ratio_val[i,3] <- perc_yes_norm
 #print(odds_ratio_val)
}
odds_ratio_val <-  odds_ratio_val[2:59,]
#print(odds_ratio_val) 
```

`r kable(odds_ratio_val)`  
  

